---
name: "Tzu-Yao Lin"
position: "Master in Psychology, National Taiwan University"
address: "3F., No. 213-1, Wuling St., Anle Dist., Keelung City 204007, Taiwan (R.O.C.)"
phone: "+886 989 878 512"
email: "r08227112@ntu.edu.tw"
github: "xup6y3ul6"
www: "Cognitive Psychometrics Lab" # change to lab name /faHeart icon
aboutme: "A committed, communicative, and team-oriented MA student in Psychology. I have a strong interest in the mathematical modeling of decision-making processes and good at statistics, data analysis, and programming. I am always eager for new knowledge and willing to share what I have learned."
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "F47F24" # 003C7D
output: 
  vitae::awesomecv:
    keep_tex: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)
source("../scripts/install.R")
```

```{r get data, include=FALSE}
## Education
education <- read_csv(here::here("data", "education.csv"))

## Awards
awards <- read_csv(here::here("data", "awards.csv"))

## Courses
courses <- read_csv(here::here("data", "courses.csv"))

## Research Experience
research <- read_csv(here::here("data", "research_experience.csv"))

## Teaching assistant
ta <- read_csv(here::here("data", "teaching.csv")) 

## Presentations
presentations <- read_csv(here::here("data", "presentations.csv")) %>% 
  arrange(desc(when))

## Skills
skills <- read_csv(here::here("data", "skills.csv")) %>% 
  group_by(category) %>% 
  mutate(skill = paste(skill, collapse = ", ")) %>% 
  ungroup %>% 
  unique

## Extracurricular Experience
extracurricular <- read_csv(here::here("data", "extracurricular_experience.csv")) 

```

# Current Research

## \begingroup\fontsize{10pt}{1em}\bodyfont\bfseries\textcolor{text} Incorporating the threshold theory into the cultural consensus theory for ordinal categorical data: A simulation study\endgroup

\begingroup\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text}

**Advisor**: Prof. Yung-Fong Hsu

Cultural consensus theory (CCT), developed by Batchelder and colleagues in the mid-1980s, is a cognitively driven methodology to assess informants' consensus in which the culturally correct answers are unknown to researchers in prior. The primary goal of CCT is to uncover the cultural knowledge, preference, or beliefs shared by members of a group. One of the CCT model, called the General Condorcet Model (GCM), deals with binary (e.g., true/false) response data which were collected from a group of informants who share the same cultural knowledge provide answers to a set of true/false questions. In my study, I try to extend the GCM with the threshold theory to account for the ordinal categorical data (including the Likert-type questionnaires) in which informants can express the different confidence levels about the items. By using the hierarchical Bayesian model, the new model is specified the item's cultural consensus truth as well as other item's response effects (e.g., item's difficulty, informant's knowledge and response bias). In this research, I used the Bayesian inference with the Markov chain Monte Carlo sampling method to evaluate the recovery of the parameters by analyzing simulated data sets.\endgroup

# Education

```{r}
detailed_entries(education,
                 when = glue("{start_date}--{end_date}"),
                 what = degree,
                 where = loc,
                 with = uni) 
```

# Awards

```{r}
detailed_entries(awards,
                 when = time,
                 what = what,
                 with = award)
```

# Graduate Level Statistics Courses

```{r}
courses %>%
  brief_entries(what = glue::glue("<code>: \\textbf{<title>}", .open = "<", .close = ">"),
                when = semester,
                with = score,
                .protect = FALSE)
```

# Research Experience

```{r research}
research %>%
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    with = topic,
    where = team,
    why = details)
```

# Presentations

```{r}
presentations %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   why = why,
                   .protect = TRUE)
```

# Teaching Assistant

```{r}
ta %>%
  brief_entries(
    what = glue::glue("<code>: \\textbf{<title>}", .open = "<", .close = ">"), 
    when = semester,
    with = score,
    .protect = FALSE)
```

# Skills

```{r}
skills %>% 
  detailed_entries(what = skill, with = category)
```

# Extracurricular Activities

```{r}
extracurricular %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   why = why,
                   .protect = TRUE)
```
