---
name: "Tzu-Yao Lin"
position: "Master in Psychology, National Taiwan University"
address: "3F., No. 213-1, Wuling St., Anle Dist., Keelung City 204007, Taiwan (R.O.C.)"
phone: "+886 989 878 512"
email: "r08227112@ntu.edu.tw"
github: "xup6y3ul6"
www: "Cognitive Psychometrics Lab" # change to lab name /faHeart icon
aboutme: "I’m a committed, communicative, and team-oriented psychology graduate student who has a strong interest in Bayesian statistics and mathematical modeling of decision-making processes. I’m good at data analysis and programming. I’m always eager for new knowledge and willing to share what I have learned."
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "0064A4" # UCI BLUE #0064A4 / UCI GOLD # FFD200
output: 
  vitae::awesomecv:
    keep_tex: TRUE
    latex_engine: lualatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)
source("../scripts/install.R")
```

```{r get data, include=FALSE}
## Education
education <- read_csv(here::here("data", "education.csv"))

## Awards
awards <- read_csv(here::here("data", "awards.csv"))

## Courses
courses <- read_csv(here::here("data", "courses.csv"))

## Research Experience
research <- read_csv(here::here("data", "research_experience.csv"))

## Training
train <- read_csv(here::here("data", "training.csv"))

## Teaching assistant
ta <- read_csv(here::here("data", "teaching.csv")) 

## Presentations
presentations <- read_csv(here::here("data", "presentations.csv")) %>% 
  arrange(desc(when))

## Skills
skills <- read_csv(here::here("data", "skills.csv")) %>% 
  group_by(category) %>% 
  mutate(skill = paste(skill, collapse = ", ")) %>% 
  ungroup %>% 
  unique

## Extracurricular Experience
extracurricular <- read_csv(here::here("data", "extracurricular_experience.csv")) 

```

# Current Research

## \begingroup\fontsize{10pt}{1em}\bodyfont\upshape\bfseries\textcolor{text} Incorporating the threshold theory into the cultural consensus theory for ordinal categorical data: A simulation study\endgroup

\begingroup\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text}

**Advisor**: Prof. Yung-Fong Hsu

Cultural consensus theory (CCT), developed by Batchelder and colleagues in the mid‐1980s, is a cognitively driven methodology to assess informants’ consensus in which the culturally correct answers are unknown to researchers in prior. The primary goal of CCT is to uncover the cultural knowledge, preference, or beliefs shared by members of a group. One of the CCT models, called the General Condorcet Model (GCM), deals with binary (e.g., true/false) response data which were collected from a group of informants who share the same cultural knowledge. I incorporated the GCM with the Luce‐Krantz threshold theory to account for ordinal categorical data (including Likert‐type questionnaires) in which informants can express different confidence levels when answering the items/questions. I applied the hierarchical Bayesian modeling approach and the Markov chain Monte Carlo sampling method to simulated data to evaluate the recovery of the parameters in the model.
\endgroup

# Education

```{r}
education %>% 
  detailed_entries(
    when = glue("{start_date}--{end_date}"),
    what = degree,
    where = loc,
    with = uni) 
```

# Awards

```{r}
awards %>% 
  detailed_entries(
    when = time,
    what = what,
    with = award,
    why = details)
```

# Graduate Level Statistics or Modeling Courses

```{r}
courses %>%
  brief_entries(
    what = glue::glue("<code>: \\textbf{<title>}", .open = "<", .close = ">"),
    when = semester,
    with = score,
    .protect = FALSE)
```

# Research Experience

```{r research}
research %>%
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    with = topic,
    where = team,
    why = details,
    .protect = TRUE)
```

# Presentations

```{r}
presentations %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    why = why,
    .protect = TRUE)
```


# Teaching Assistant

```{r}
ta %>%
  brief_entries(
    what = glue::glue("<code>: \\textbf{<title>}", .open = "<", .close = ">"), 
    when = semester,
    with = score,
    .protect = FALSE)
```

# Training
```{r}
train %>% 
  detailed_entries(
    what = what, 
    when = when,
    with = with,
    where = where,
    .protect = TRUE)
```


# Skills

```{r}
skills %>% 
  detailed_entries(
    what = skill, 
    with = category,
    .protect = FALSE)
```

# Extracurricular Activities

```{r}
extracurricular %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    why = why,
    .protect = FALSE)
```
